\chapter{Introduction}
\label{ch:introduction}

\section{Introduction}
\label{sec:introduction}

Effective communication is essential for every person throughout every stage of their life. That is why speech development at an early age plays a fundamental role in children's ability to talk, understand social behaviour, and engage in learning environments. Unfortunately, approximately 1 in 14 children ages 3--17 has had a disorder related to voice, speech, or language in the past 12 months \cite{nidcd_statistics}. When children develop speech impairments, they may struggle to express themselves clearly, leading to lowered confidence and fewer interactions with their peers. Speech therapy can help address these challenges, but progress generally depends on frequent and consistent practice over time, not only during scheduled therapy sessions.

Research suggests that therapy intensity and consistency can significantly affect outcomes for children with speech sound disorders. In a randomised study, Allen (2013) compared preschool children receiving phonological intervention three times per week with children receiving the same intervention once per week. The higher-frequency group showed significantly greater gains in percentage of consonants correct, while the once-weekly group's progress was similar to the active control group. This supports the idea that regular, frequent practice may lead to better speech improvement than less consistent or lower-frequency intervention \cite{allen2013intervention}.

In practice, however, this creates a logistical challenge. Professional speech therapy sessions are limited in duration and frequency, and exercises performed at home may be difficult to sustain consistently or execute correctly. Children may not have the motivation to practise, or they may lose it once the exercises feel repetitive. Parents or caregivers may not always have the needed tools, time, or structure to support effective home practice. This gap between clinical sessions and home practice creates a real-world and well-defined problem for a software engineering project: how can a digital tool help bridge that gap in a way that is accessible, structured, and engaging for young users?

This bachelor project delves into the design and implementation of a two-component software system intended to support children with speech impairments through guided, interactive practice. The system combines a mobile application, through which children complete speech-related exercises, with a web-based therapist dashboard, through which speech therapists can create and assign exercises and monitor each child's progress. The exercise content in the mobile application is inspired by established literature on articulation disorders \cite{todorova_articulation} and includes diverse ways of practising. The application provides feedback to the child upon completing exercises, supporting engagement and a sense of progression.

The proposed system is not intended to replace professional speech therapists. Instead, it aims to act as a supplementary tool that makes structured speech practice more accessible between therapy sessions. The project therefore considers both the implementation of the system and the broader software engineering practices needed to develop it successfully.

The remainder of this report is structured as follows: \Cref{ch:project-background} presents the project background and defines the scope of the work. \Cref{ch:problem-statement} introduces the problem statement and motivates why the selected problem is relevant. \Cref{ch:proposed-solution} describes the proposed solution and explains the reasoning behind the chosen approach. \Cref{ch:implementation} presents the implementation, including the technologies, system components, and results. \Cref{ch:software-engineering-practices} discusses the software engineering practices used throughout the project. \Cref{ch:discussion} reflects on the effectiveness of the solution, challenges encountered, and lessons learned. Finally, \Cref{ch:conclusion} concludes the report by summarising the project and its main outcomes.
