\chapter{Project Background}
\label{ch:project-background}

\section{Project Background}
\label{sec:project-background}

Currently, the available products on the market that address our problem are basic, not supported by their creators or morally out of date. The usage of said applications is recommended by a small part of the speech therapist. The current state of applications is also either hard for children to understand or so basic that it practically has no effect on their speech improvement.
\linebreak

The applications are falling behind because this problem has rarely been addressed. Many therapists assign homework to their children to be done with supervision at home by their parents. Unfortunately, Parents often don’t have the needed time to supervise their children during homework. This leaves children not being able to get feedback or help needed at home. This missing aspect is what can be addressed with an modernized and up-to-date application to supervise children and provide therapists with analysis of the work done.
\linebreak

Our project aims to provide the children with a modern gamified application that attracts their attention and provides them with a fun learning experience to retain their attention. Behind the gamification of our application is providing children with a simple and fun-made explanation on their exercises, problems, wrong or correct answers. This ensures that the child gets feedback on his progress. Another thing the application collects and provides is the data to the therapist who can easily check the child’s progress and follow-up with it. The therapist has utmost control of the child’s roadmap to the solution of his speech impairment with the options available in the dashboard.
tended to support, rather than replace, the role of the professional speech therapist.

\subsubsection*{Key Deliverables}

\begin{itemize}
    \item A mobile application for children that provides guided, interactive, and gamified speech practice exercises.
    \item A web-based therapist dashboard that allows therapists to create, assign, and manage exercises for individual children.
    \item A database-backed system for storing user information, assigned exercises, completed tasks, and progress data.
\end{itemize}

\subsubsection*{Expected Outcomes}

\begin{itemize}
    \item Children are provided with a more engaging and structured way to practise speech exercises outside therapy sessions.
    \item Therapists are able to monitor each child’s progress and adapt the assigned exercises based on performance data.
    \item The gap between professional therapy sessions and home practice is reduced through a digital tool that supports consistency, feedback, and motivation.
\end{itemize}

\section{Project Scope}

The application is giving the child a game-like app to use, play and learn without the need for advanced options, exercises or design. It is made in a simple, basic and fun way for children. It focuses on end-to-end development with a mobile application that can be controlled with a web-based dashboard for the therapist. Every data needed for the application and the dashboard is stored on a database connected and ensures real-time syncing.