\chapter{Software Engineering Practices}
\label{ch:software-engineering-practices}

This chapter describes the software engineering practices used for developing the project. The purpose was not only to build the working prototype but to design it in a structured way that is easily maintainable, allows for future expansion, and demonstrates core principles from software engineering and software architecture.

\section{Software Design and Architecture Design Principles}
\label{sec:software-design-and-architecture-design-principles}

The system was designed as a multi-component application consisting of a Unity mobile client, a Django backend, a therapist web dashboard, and a Supabase PostgreSQL database. This decoupling was a key design decision, as each part of the system has a different responsibility, as outlined in \Cref{ch:implementation}, minimizing dependencies between components. An example of that would be that the Unity application does not directly access the database, yet receives the data it wants successfully. The design also follows the separation of concerns principle, distributing functionality across smaller parts rather than placing it all in a single application. Further benefits include easier maintainability, faster development speed, and lower overhead for future expansion. For instance, if there are changes to the internal data structure, it does not require changes as long as the API responses remain intact.

Another important design decision was to decouple larger parts of the system and avoid breaking the Single-Responsibility Principle. To illustrate, the exercise orchestrator controls the flow of the exercises while separate components handle the JSON parsing, animation, scene loader, answer panel, audio loading, and API communication.

The system was also designed to be highly scalable and modular. The current prototype supports the main project workflow, but the architecture enables future development, including additional exercise types, richer progress tracking, stronger child authentication, offline support, and more advanced pronunciation feedback. This was important because the project is a prototype, but it should still provide a foundation that can be continued.

The layered architecture of the application separates the system into levels of responsibility, extending the architecture described in \Cref{sec:system-architecture}. The three main layers are as shown:

\begin{itemize}
    \item \textbf{Presentation layer:} The presentation layer consists of the Unity client and the therapist web app. Those are the parts of the system that the user interacts with directly.
    \item \textbf{Application/backend layer:} The application/backend layer contains the business logic of the system: authentication handling, exercise retrieval, CRUD operations, session result submission, and dashboard data.
    \item \textbf{Data layer:} The data layer is the PostgreSQL database. It stores persistent data, including therapists' credentials, children, exercises, assignments, completed sessions, and more.
\end{itemize}

The layered approach is functional at keeping responsibilities separate, as the user interface does not need to know how data is stored internally, the database does not need to know how Unity displays the exercises, and the backend acts as the middle layer that connects these parts.

\section{Scrum and Agile Team Organization}
\label{sec:scrum-and-agile-team-organization}

The project's development lifecycle followed the Agile methodology, using the Scrum framework. Scrum is a project management framework that breaks down the cycle of developing a software product from a single timeline into several small timeline cycles called sprints. This methodology was chosen over traditional linear methods, such as Waterfall, as it provided the team with the flexibility needed for prototype development. Sprints allowed the team to adapt to arising challenges. It also gave a way for the received feedback to be included in further sprints, allowing the prototype to evolve according to the users' expectations. The sprints were structured in either one- or two-week cycles. Every sprint was dedicated to a particular feature or issue. Our sprints also included the time needed for research, such as our problem formulation.

While the lifecycle of development followed Agile Scrum, the testing of the prototype adhered to the Verification and Validation principles of the V-model. The V-model is a traditionally linear testing framework stating that every development phase needs to have a corresponding testing phase. This model was adapted to fit into the team's sprint timelines. This approach was chosen because the project relies on asynchronous data routing between Unity, Django, and the database. To ensure data integrity across these components, we required immediate checks. As components were designed and implemented, the corresponding unit and integration tests were planned and executed. Before every sprint's start, the code was verified through member-reviewed pull requests in GitHub. This approach guaranteed that the code written consistently met the set requirements and integrated without slowing down the pace of Agile development.

To utilize the Scrum framework, the team chose Jira as the primary project management software. The platform provided the members with issue-tracking tools that helped us visualize the workflow inside a Scrum board. The usage of this board was crucial to maintain transparency and to track the overall project's velocity. This ensured the team members did not overlap or interfere with each other's tasks. When a new sprint started, each goal was broken down and split into several tasks. These tasks were assigned to team members and transitioned over their respective lifecycle phases. Using Jira, the team had a real-time visualization of every task's status and each sprint's progress.

To ensure the system remained relevant to its target audience, the team's initial step was to envision the end users. This was done by developing user personas representing the profiles and archetypes of target users. These profiles were paired with user stories created to represent complex features in a natural, simple way, told from the users' perspective. Together, these formed the requirements that guided the system toward addressing the real-world needs of its end users, rather than relying on assumptions. By mapping specific requirements of both SLPs and patients, a clearer problem foundation was established. They also informed the proposed solutions and prioritized feature development.

\section{Testing and Quality Assurance}
\label{sec:testing-and-quality-assurance}

Quality assurance was handled through a combination of version control, pull requests, unit testing, code reviews, and task tracking.

GitHub was used for version control and collaboration. The team used two separate repositories, one for the Unity client and one for the web client, for easier codebase understanding. Team members developed their features on separate branches, which were then reviewed and tested by another team member through pull requests. Once the reviewer confirmed that tests were successful, only then was the branch merged into main. This allowed the team to work independently on the latest version of the project without threatening to compromise the system.

Unit tests were used both in the Django backend and Unity's main functionality. Tests covered important backend workflows as well as essential database-related behavior such as retrieving dashboard data, CRUD operations, exercise assignment and unassignment, and storing session data. For example, when an exercise is unassigned from a child, the assignment should be removed or updated in the database. When Unity submits a session result, the backend should store it correctly. When the therapist creates or edits an exercise, the changes should be saved and applied to the database. These tests helped verify that the backend behaved as intended and code changes did not break the core.

End-to-end testing was also necessary, as the system includes many user-facing interactive interfaces. The therapist dashboard was tested manually in the browser by checking the login dashboard, loading the child profile, exercise CRUD operations, assignment, and unassignment. Every exercise in Unity was then thoroughly tested to ensure the user flow was intuitive and easy to operate.

Additionally, core Unity logic was unit tested, focusing mainly on the JSON-driven exercise system and verifying that the templates can be parsed correctly into the expected exercise, options, and word packages. The generated coverage report summarized in \Cref{tab:unity-selected-coverage} shows that the targeted test has good line coverage of the core \texttt{Exercise\_JSON\_Parser}, reaching a little over 84\%. The test assembly is fully covered, reaching 100\%.

\begin{table}[H]
    \centering
    \caption{Unity coverage report summary.}
    \label{tab:unity-coverage-summary}
    \begin{tabular}{ll}
        \toprule
        \textbf{Metric} & \textbf{Result} \\
        \midrule
        Generated on & 2026-05-23 17:25 \\
        Assemblies & 2 \\
        Classes & 147 \\
        Files & 127 \\
        Covered lines & 286 \\
        Uncovered lines & 12,723 \\
        Coverable lines & 13,009 \\
        Total lines & 24,042 \\
        Line coverage & 2.1\% (286 of 13,009) \\
        Covered methods & 82 \\
        Total methods & 1,929 \\
        Method coverage & 4.2\% (82 of 1,929) \\
        \bottomrule
    \end{tabular}
\end{table}

\begin{table}[H]
    \centering
    \caption{Selected Unity class coverage results.}
    \label{tab:unity-selected-coverage}
    \begin{tabular}{lrrrr}
        \toprule
        \textbf{Class} & \textbf{Covered} & \textbf{Uncovered} & \textbf{Coverable} & \textbf{Coverage} \\
        \midrule
        Exercise\_JSON\_Parser & 127 & 23 & 150 & 84.6\% \\
        ExerciseScoreCalculator & 6 & 0 & 6 & 100\% \\
        Exercise & 13 & 4 & 17 & 76.4\% \\
        Word\_Package & 8 & 7 & 15 & 53.3\% \\
        Option\_Text & 13 & 0 & 13 & 100\% \\
        Option\_Multiple\_Choice & 7 & 0 & 7 & 100\% \\
        Option\_Groups & 7 & 0 & 7 & 100\% \\
        Pronunciation\_Sound & 9 & 0 & 9 & 100\% \\
        Tests / ExerciseJsonParserTests & 79 & 0 & 79 & 100\% \\
        \bottomrule
    \end{tabular}
\end{table}

\begin{table}[H]
    \centering
    \caption{Django backend coverage report summary.}
    \label{tab:django-coverage-summary}
    \begin{tabular}{lrrrr}
        \toprule
        \textbf{File} & \textbf{Statements} & \textbf{Missing} & \textbf{Excluded} & \textbf{Coverage} \\
        \midrule
        therapy/\_\_init\_\_.py & 0 & 0 & 0 & 100\% \\
        therapy/admin.py & 9 & 0 & 0 & 100\% \\
        therapy/apps.py & 4 & 0 & 0 & 100\% \\
        therapy/forms.py & 6 & 0 & 0 & 100\% \\
        therapy/models.py & 67 & 0 & 0 & 100\% \\
        therapy/urls.py & 3 & 0 & 0 & 100\% \\
        therapy/views.py & 175 & 34 & 0 & 81\% \\
        \midrule
        Total & 264 & 34 & 0 & 87\% \\
        \bottomrule
    \end{tabular}
\end{table}

The Unity coverage report shows low overall line coverage because the Unity project contains many UI, scene, third-party, and MediaPipe-related scripts that were tested manually rather than through automated unit tests. The targeted Unity tests focused on the JSON-driven exercise system, where the parser and data model classes achieved substantially higher coverage. The Django backend coverage was higher overall because backend behavior such as models, routes, dashboard APIs, CRUD operations, assignment handling, and session storage is more suitable for automated unit testing.
